Analysis the leading causes of death in Alberta

### 2024-03-17 output/paper/paper.qmd
final change

This paper is carried out using statistical programming language `R` [@citeR], the library `tidyverse` [@tid] for preparation and analysis of data, the `janitor` [@jan], the `here` [@here] for read data, the `ggplot2` for generating figures, the `dplyr` [@dp], and we run the model in `R` [@citeR] using the `rstanarm` package [@rstanarm], the `boom` package [@boom], and the `boom.Mixed` package [@bm]. Since this paper is a reproduction of 'Telling Stories with Data' [@alexander_2023], some similar code were used.

@@

Firstly, we can get the Poisson probability mass function which is same as the negative binomial is [@pitman_1993] $$ 
P(X=k)= e^{-λ}λ^k/k!, for\\k = 0,1,2,3,...
$$

@@

$$ 
y_{i}|λ_{i} \sim Poisson \\
log_{e}(λ_{i}) = β_{0} + β_{1} \times cause_{i}
$$

@@

Firstly, since $$ 
y_{i} = e^{log_{e}(λ_{i})}
$$ We can have two equations such that $$ 
y_{i} = e^{log_{e}(λ_{i})} = e^{7.037 + 0.446I_{1} + 0.224I_{2} + 0.046I_{3}}, for\ Poisson \ Model\\
y_{i} = e^{log_{e}(λ_{i})} = e^{7.039 + 0.446I_{1} + 0.221I_{2} + 0.043I_{3}}, for\ Negative\ Binomial\ Model
$$ where

>>>>

This paper is carried out using statistical programming language `R` [@citeR], the library `tidyverse` [@tid] for preparation and analysis of data, the `janitor` [@jan], the `here` [@here] for read data, the `ggplot2` for generating figures, the `dplyr` [@dp], and we run the model in `R` [@citeR] using the `rstanarm` package [@rstanarm], the `broom` package [@broom], and the `broom.Mixed` package [@bm]. Since this paper is a reproduction of 'Telling Stories with Data' [@alexander_2023], some similar code were used.

@@

Firstly, we can get the Poisson probability mass function which is same as the negative binomial is [@pitman_1993]

$$ 
P(X=k)= e^{-λ}λ^k/k!, for\ k = 0,1,2,3,...
$$

@@

$$ 
y_{i}|λ_{i} \sim Poisson
$$
$$
log_{e}(λ_{i}) = β_{0} + β_{1} \times cause_{i}
$$

@@

$$ 
y_{i} = e^{log_{e}(λ_{i})}
$$
$$
y_{i} = e^{log_{e}(λ_{i})} = e^{7.037 + 0.446I_{1} + 0.224I_{2} + 0.046I_{3}}, for \ Poisson \ Model
$$
$$
y_{i} = e^{log_{e}(λ_{i})} = e^{7.039 + 0.446I_{1} + 0.221I_{2} + 0.043I_{3}}, for \ Negative \ Binomial\ Model
$$

where
